PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-13 paper/paper.tex
Appendix B done, modulo final Z pT results
Acknowledgements

\usepackage[UKenglish]{babel}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage[binary-units=true,detect-weight=true,table-format=4.2]{siunitx}
\usepackage{xcolor}
\usepackage[percent]{overpic}
\usepackage{mathcomp}
\usepackage{tabularx}

\newcommand{\alphas}{\alpha_\mathrm{s}}
\preprint{Nikhef-2020-026 TIF-UNIMI-2020-22}

@@

\acknowledgments
We are grateful to Rikkert Frederix for discussions and explanations about
\textsc{aMCfast}. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data.
%Alessandro Vicini\\
%Stefan Dittmaier
E.R.N.\ is supported by the European Commission through a Marie
Sk\l odowska-Curie Action (grant agreement no.\ 752748).
C.S.\ and S.C.\ are supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
MZ thanks the Nikhef institute in Amsterdam,
where he was employed during the early stages of this paper.

>>>>

\usepackage[UKenglish]{babel}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage[binary-units=true,detect-weight=true,table-format=4.2]{siunitx}
\usepackage{xcolor}
\usepackage[percent]{overpic}
\usepackage{mathcomp}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{xltabular}

\newcommand{\alphas}{\alpha_\mathrm{s}}
\DeclareSIUnit\permille{\text{\textperthousand}}

\preprint{Nikhef-2020-026 TIF-UNIMI-2020-22}

@@

\acknowledgments
We are grateful to Rikkert Frederix for discussions about
\textsc{aMCfast}, and to Stefan Dittmaier for a critical reading of the
manuscript. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data.
%Alessandro Vicini\\
S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
E.R.N.\ is supported by the European Commission through a Marie
Sk\l odowska-Curie Action (grant agreement no.\ 752748).
M.Z.\ thanks the Nikhef institute in Amsterdam,
where he was employed when this paper was started.
